---
title: "Everest Bio"
output: 
  flexdashboard::flex_dashboard:
    #storyboard: true
    orientation: rows
    logo: https://raw.githubusercontent.com/fabbiocrux/Figures/main/Everest-bio/logos/favicon-tool.png
    #vertical_layout: scroll
    social: menu
#date: "Version of the Document:  `r format(Sys.time(), '%d %B, %Y')`" 
#author: "Université de Lorraine"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  include=FALSE, warning = FALSE, message = FALSE)
#source()
library(leaflet)

```


# Goal {.sidebar data-icon="fa-signal"}
**Goal of WP 4.1 :**

> The main purpose of task 4.1 is to describe and define the needs of each demonstrator in order to establish a common base. Thus, each physical demonstrator shall be observed, and specific data of the processes shall be collected with the purpose to create a holistic framework of open manufacturing demonstration facility.

<a href = "https://erpi.univ-lorraine.fr/">Made by Université de Lorraine</a>


# DIT {data-icon="fa-bullseye"}
## Row {.tabset .tabset-fade}
### Global DIT process

![Do-It-Together Process](www/images/DIT.svg)

### Local Ecosystem 
```{r}

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="Lorraine Fab Living Lab")
m  # Print the map

```

### Specific DIT Process
```{r}

```



# Global analysis {data-icon="fa-diagnoses"} 
## Row {.tabset .tabset-fade}

### Impact Matrix    
```{r}

```


### Global DIT Vs. Use cases

```{r}

```


### Specific DIT Vs. Use cases





# AIMEN  {data-icon="fa-id-card"}

Row {.tabset .tabset-fade}
-------------------------------------
   
### Global Description
```{r}

```


### Expected results
```{r}

```



### Innovations
```{r}

```


### Impacts
```{r}

```





# UL  {data-icon="fa-id-card"}
## Row {.tabset .tabset-fade}

### Global Description
```{r}

```


### Expected results
```{r}

```


### Innovations
```{r}

```


### Impacts
```{r}

```




# UNINOVA  {data-icon="fa-id-card"}
## Row {.tabset .tabset-fade}

### Global Description
```{r}

```

### Expected results
```{r}

```

### Innovations
```{r}

```

### Impacts
```{r}

```




