---
title: "Everest Bio"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
# output: 
#   flexdashboard::flex_dashboard:
#     #storyboard: true
#     orientation: rows
#     logo: https://raw.githubusercontent.com/fabbiocrux/Figures/main/Everest-bio/logos/favicon-tool.png
#     #vertical_layout: scroll
#     social: menu
#date: "Version of the Document:  `r format(Sys.time(), '%d %B, %Y')`" 
#author: "Université de Lorraine"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, warning = FALSE, message = FALSE, cache = FALSE)
#source()
library(leaflet)
library(tidyverse)
library(shiny)
library(shinyWidgets)
library(readxl)
library(here)

# Link for the Figures
URL = c('https://raw.githubusercontent.com/fabbiocrux/Figures/main/')

```





```{r CICES, include=FALSE, echo=FALSE}

CICES <- read_excel(here("CICES/CICES-Questionnaire.xlsx"), sheet = "CICES V5.1",  skip = 4 )
names(CICES)

# Filtering only CICES
CICES <- CICES %>% filter(Filter == "CICES")


# Ordering the Factors
Test <- CICES %>%
  mutate(Division = factor(Division, CICES %>% pull(Division) %>% unique())) %>% 
  mutate(Group = factor(Group, CICES %>% pull(Group) %>% unique())) %>% 
  mutate(Labels = factor(Labels, CICES %>% pull(Labels) %>% unique())) %>% 
  mutate(Question_Territorial = factor(Question_Territorial)) %>% 
  mutate(ID_Q = tolower(gsub(" ","", Labels))) %>% 
  mutate(ID_Q = tolower(gsub(",","", ID_Q))) 

# Fill the Voids 
Test <- Test %>%  
  fill(Question_Territorial) %>% 
  fill(Question_Entreprise) %>% 
  fill(Questions) %>% 
  fill(Labels) %>% 
  fill(ID_Q)

# Creating ID
Test <- Test %>%  mutate(ID = Code) 
  

A <- Test %>% filter(Questions == "A")
B <- Test %>% filter(Questions == "B")

# Funciones para el cuestionario
source("R/ES_Preguntas.R")
source("R/ES_Division.R")
source("R/ES_Descriptor.R")
source("R/ES_Questions.R")

#Veryfing the levels
#Test$ID %>% as.factor() %>% levels()


# Preguntas <- 
#       Test %>% 
#       group_by(Section, Division, Group ) %>% tally()
      #filter(Group == Grupos[j]) %>% 
      #filter(Labels == Labels[j]) 

#Preguntas <- Preguntas %>% left_join(Test %>% pull(Section, Division))  %>% select(Section, Division:n)    
      
```

## Presentation

### Goal of Everest Bio : 

> To develop a generic methodology to assess the **ecosystem services** rendered by industrial activities operating in short circuit in order to improve decision-making by industrial and public actors. 


<a href = "https://erpi.univ-lorraine.fr/">Made by Université de Lorraine</a>

## Consentement

>Here we will pute the consentement according to the GRPD

## Let's us know your profile

### Who you are?


```{r}
fluidPage(
  awesomeRadio(
   inputId = "Perfil",
   label = "Your profile is:", 
    choices = c("Territorial agent"="Territorial", "Entreprise agent"="Entreprise", "Citizen"="Citizen"),
   #selected = "B",
   status = "warning"
)
)
```


```{r, context="server"}
observeEvent(input$Perfil, {
   cat("Selection is:", input$Perfil )
  })


output$Question <- renderUI({
  
 if (input$Perfil  == 'Territorial') {
    h4(vars$Question_Territorial[1]) 
    #vars <-  vars %>% mutate(Questions_description = Question_Territorial)
    #paste("You have selected", input$Perfil)
   } else if (input$Perfil == 'Entreprise') {
     h4(vars$Question_Entreprise[1]) 
     #vars <-  vars %>% mutate(Questions_description = Question_Entreprise)
   }
})

# 
# output$Question <- renderUI({
# 
#   column(4, vars %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
#   switchInput(inputId = ID_Q,
#                label = Labels, 
#                onStatus = "success",
#                offStatus = "danger",
#                onLabel = "Yes",
#                offLabel = "No"
#    )
# 
# 
# })

#vars <- Test %>% filter(Questions == "A") 
#vars <- reactive(Test)
```


## ES: Provisioning

### Biomass

In the following questions, please check the variables that are true for you case


```{r Biomass_Plants, eval=TRUE, include=TRUE}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "A") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  #
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```



```{r Biomass_Animals,}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "B") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```



```{r Biomass_Wild,}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "C") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```

### Genetic material from all biota (including seed, spore or gamete production)

```{r}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "D") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```


                                            

## ES: Regulation & Maintenance (Biotic)


### Transformation of biochemical or physical inputs to ecosystems

```{r}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "F") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```


### Regulation of physical, chemical, biological conditions

```{r}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "G") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)


```



## ES: Cultural & Information

### Direct, in-situ and outdoor interactions with living systems that depend on presence in the environmental setting

```{r}
# Filtering the dataframe
vars <- Test %>% filter(Questions == "H") 
fluidPage(
fluidRow( 
  #uiOutput("Question"),
  column(4, vars  %>% select(Labels, ID_Q)  %>% unique()  %>% pmap(. , ES_Division)) ,
  column(8, vars  %>% select(Labels,ID_Q, ID, `Simple descriptor`)  %>%  pmap(. , ES_Descriptor))
  ),
hr()
)
```

## REsults

                                                     
```{r}
fluidPage(
fluidRow( 
  actionButton("submit", "Submit"),
  
 tableOutput("responses")
 )
)
```




```{r, context="server"}
# observeEvent(input$`1.1.1.1`, {
#    cat("Selection is:", input$`1.1.1.1` )
#   })
# 
# 
# output$Table <- renderUI({
#   
#  if (input$Perfil  == 'Territorial') {
#     h4(vars$Question_Territorial[1]) 
#     #vars <-  vars %>% mutate(Questions_description = Question_Territorial)
#     #paste("You have selected", input$Perfil)
#    } else if (input$Perfil == 'Entreprise') {
#      h4(vars$Question_Entreprise[1]) 
#      #vars <-  vars %>% mutate(Questions_description = Question_Entreprise)
#    }
# })


saveData <- function(data) {
  data <- as.data.frame(t(data))
  if (exists("responses")) {
    responses <<- rbind(responses, data)
  } else {
    responses <<- data
  }
  
  write_csv(responses, "respuestas.csv")
}

loadData <- function() {
  if (exists("responses")) {
    responses
  }
}

# Whenever a field is filled, aggregate all form data
formData <- reactive({
    data <- sapply(Test$ID, function(x) input[[x]])
      data
})
      
# When the Submit button is clicked, save the form data
observeEvent(input$submit, {
  saveData(formData())
})


# Show the previous responses
    # (update with current response when Submit is clicked)
    output$responses <- DT::renderDataTable({
      input$submit
      loadData()
    })     

  
```



